Performance of two different ontological and data access methods

### 2014-07-06 cold2014/magnus.tex
Removed chunk in ten factor experiment
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@738 43ef1190-90fd-4dd7-a769-d0121f02b80e

Like the rest of the experiments we used DanielPlot to evaluate and a
package in R to visualize the result. Figure~\ref{3factorGraph}
shows only one significant factor, namely the \textsf{O} factor in the
upper right corner. In Table~\ref{3factorEffect}
we can see the time effects from largest to smallest.  We see that the
ontology factor has the largest effect on approximately 2.2 seconds
which means that one of the ontologies overall is 2.2 seconds
faster. By reading the results from the linear model it is the factor
level \textsf{-vso} which has an overall faster response time.

@@

\subsubsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.   % TODO: Explain more how the levels were set?
With 10 factors the amount of
runs were $2^{10}$, which made the planning matrix too big to show here. 
To determine the levels of each factor, we calculated the average value 
of each factor present in the data sets.

In the graph~\ref{10factorGraph} we can see the results from running
all the 1024 runs.  We can see that there are a lot of significant
effects present here. 
Unfortunately there are so many significant factors that there are
some of them that are illegible, but most of them have a low impact on
the significance graph.  In Table~\ref{10factorEffect} we can see the top
fifteen absolute effects. We can see that emission and fuel consumption are 
the most significant factors besides the ontology factor.
The linear model again tells us that the option
\textsf{-vso} has a significantly lower response time than
\textsf{-co}

When we accumulated the results from all the runs we ended up with the
total amount of response time to be approximately 30095 seconds, which
is 8 hours, 21 minutes and 35 seconds.  This were the total response
time after running all the runs. This did not take into account all
the other steps during the experiments which took time, like writing
results to file and initiating the application.  This discouraged the
replication of the experiment due to the size and was also a reason
why we did not do experiments with more factors.

>>>>

Figure~\ref{3factorGraph}
shows only one significant factor, namely the \textsf{O} factor in the
upper right corner. In Table~\ref{3factorEffect}
we can see the time effects from largest to smallest.  We see that the
ontology factor has the largest effect on approximately 2.2 seconds
which means that one of the ontologies overall is 2.2 seconds
faster. By reading the results from the linear model it is the factor
level \textsf{-vso} which has an overall faster response time.

@@

\subsubsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.  
With 10 factors the amount of
runs were $2^{10}$, which made the planning matrix too big to show here. 
To determine the levels of each factor, we calculated the average value 
of each factor present in the data sets.

In the graph~\ref{10factorGraph} we can see the results from running
all the 1024 runs.  We can see that there are a lot of significant
effects present here. 
Unfortunately there are so many significant factors that there are
some of them that are illegible, but most of them have a low impact on
the significance graph.  In Table~\ref{10factorEffect} we can see the top
fifteen absolute effects. We can see that emission and fuel consumption are 
the most significant factors besides the ontology factor.
The linear model again tells us that the option
\textsf{-vso} has a significantly lower response time than
\textsf{-co}.
